Stage-Splitting a Modal Language

### 2014-07-24 paper/splitting.tex
minor changes after meeting with nico
A few changes to metatheory sections.
beginning to generalize the splitting correctness theorems

>>>>

\subsection{Value Splitting, Etc}

...

\subsection{Metatheory}

\begin{definition}
For residuals $q_1$ and $q_2$, define $q_1 \le_\beta q_2$ (``$q_1$ is $\beta$-smaller than $q_2$'') if they are
identical modulo internal beta reductions of $q_2$.
\end{definition}

The theorem we really want is this:

\begin{theorem}
If $\cdot\vdash e : A \splittwosym [p,l.r]$ then,
\begin{itemize}
\item $\cdot \vdash e : A~@~\bbtwo$ and
\item $\types [l:\tau] r A$ and
\item $\diatwo [\cdot] e q$ iff $\reduce p u$ and if so
\item $q \le_\beta (\letin{l}{u}{r})$
\end{itemize}
\end{theorem}

But this isn't strong enough to prove on its own.  
Firstly, it only considers empty contexts, which is not enough.
Second, it is only at the second stage.

Here's an empty-context version for the first stage.

\TODO fix below
\begin{theorem}
If $\cdot\vdash e : A \splitonesym [c,l.r]$ then,
\begin{itemize}
\item $\cdot \vdash e : A~@~\bbtwo$ and
\item $\types [l:\tau] r A$ and
\item $\diatwo [\cdot] e q$ iff $\reduce p u$ and if so
\item $q \le_\beta (\letin{l}{u}{r})$
\end{itemize}
\end{theorem}

\input{figures/splitting-misc}
